Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Remove text we don't use
All different
Are we still doing phrasing?

The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however
whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
(Although when we filter by paths we make use of the complement rather than the loop complement.)
The following proposition follows directly from the definitions.

@@

Constraints are used to ensure that adjacency pairs of vertices are mapped to adjacenct pairs of
vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
is also permitted.  To handle the induced case, rather than the more usual approach of directly
having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
\rightarrowtail \loopcomp{T}$.

?? All different.

For subgraph isomorphism, we can do domain filtering at the top of search, to reduce the initial
sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph isomorphism also
allows us to generate additional implied constraints, which we discuss in
\cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph
problem.

>>>>

The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however
whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
The following proposition follows directly from the definitions.

@@

Constraints are used to ensure that adjacency pairs of vertices are mapped to adjacenct pairs of
vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
is also permitted.  To handle the induced case, rather than the more usual approach of directly
having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
\rightarrowtail \loopcomp{T}$. Finally, an all different except $\bot$ constraint ensures
injectivity.

For subgraph isomorphism, this model can be enhanced with domain filtering at the top of search, to
reduce the initial sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph
isomorphism also allows us to generate additional implied constraints, which we discuss in
\cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph
problem.
